{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-06 Paper/main.tex
Auto stash before merge of "main" and "origin/main"

	\subsection{Inner Products and Hilbert Spaces}
	Let $\mathbb{V}$ be a vector space over some field of scalars $\mathbb{F}$. In the following we restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$. A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.

>>>>

	\subsection{Inner Products and Hilbert Spaces}
	In the following we restrict our analysis to vector spaces over $\mathbb{R}$ but more a general formalization including other fields is possible. Let $\mathbb{V}$ be a vector space over $\mathbb{R}$.  Then, a function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{R}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{R}$ the following properties hold.
